A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2019-07-29 paper/data/boxPlotsWithTikz.tex
finished first set of figures

\pgfplotscreateplotcyclelist{mylist}{%
{black,thick,smooth},
{black!50!white,thick,smooth},
{black,thick,densely dashed,smooth},
{black!50!white,thick,densely dashed,smooth},
{black,double,smooth}
}

@@

\addplot[name path=rm_u,black,smooth] table [x=n, y=cr_up rm, col sep=semicolon]{crossingResolution.csv};
\addplot[name path=rm_d,black,smooth] table [x=n, y=cr_down rm, col sep=semicolon]{crossingResolution.csv};
\addplot[black!50,fill opacity=0.5] fill between[of=rm_u and rm_d];

\addplot[name path=rm-1_u,black!50!white,smooth] table [x=n, y=cr_up rm-1, col sep=semicolon] {crossingResolution.csv};
\addplot[name path=rm-1_d,black!50!white,smooth] table [x=n, y=cr_down rm-1, col sep=semicolon] {crossingResolution.csv};
\addplot[black!25,fill opacity=0.5] fill between[of=rm-1_u and rm-1_d];

\addplot[name path=fa_u,black,smooth,densely dashed] table [x=n, y=cr_up fa, col sep=semicolon]{crossingResolution.csv};
\addplot[name path=fa_d,black,smooth,densely dashed] table [x=n, y=cr_down fa, col sep=semicolon]{crossingResolution.csv};
\addplot[black!50,fill opacity=0.5] fill between[of=fa_u and fa_d];

>>>>

\pgfplotscreateplotcyclelist{mylist}{%
{blue,thick,smooth},
{red,thick,smooth},
{green!70!black,thick,smooth},
{blue!50!red,thick,smooth},
{black,double,smooth}
}

@@

\addplot[name path=rm_u,blue,smooth,opacity=0.175] table [x=n, y=cr_up rm, col sep=semicolon]{crossingResolution.csv};
\addplot[name path=rm_d,blue,smooth,opacity=0.175] table [x=n, y=cr_down rm, col sep=semicolon]{crossingResolution.csv};
\addplot[blue!80,fill opacity=0.1] fill between[of=rm_u and rm_d];

\addplot[name path=rm-1_u,red!80,smooth,opacity=0.175] table [x=n, y=cr_up rm-1, col sep=semicolon] {crossingResolution.csv};
\addplot[name path=rm-1_d,red!80,smooth,opacity=0.175] table [x=n, y=cr_down rm-1, col sep=semicolon] {crossingResolution.csv};
\addplot[red!80,fill opacity=0.1] fill between[of=rm-1_u and rm-1_d];

\addplot[name path=fa_u,green!70!black,smooth,opacity=0.175] table [x=n, y=cr_up fa, col sep=semicolon]{crossingResolution.csv};
\addplot[name path=fa_d,,green!70!black,smooth,opacity=0.175] table [x=n, y=cr_down fa, col sep=semicolon]{crossingResolution.csv};
\addplot[green!70!black,fill opacity=0.1] fill between[of=fa_u and fa_d];

\addplot[blue,smooth,thick] table [x=n, y=crossing resolution rm, col sep=semicolon]{crossingResolution.csv};
\addplot[red,smooth,thick] table [x=n, y=crossing resolution rm-1, col sep=semicolon] {crossingResolution.csv};
\addplot[green!70!black,smooth,thick] table [x=n, y=crossing resolution fa, col sep=semicolon]{crossingResolution.csv};
\addplot[blue!50!red,smooth,thick] table [x=Nodes, y=Crossing Only, col sep=semicolon]{abs-crossingResolution.csv};
